Unshuffling Permutations

### 2015-09-12 article.tex
reduction

\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
%\usepackage{llncsdoc}
\usepackage[english]{babel}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage{shuffle}

@@

  \begin{proof}[of Claim~\ref{claim:one (nu_2, nu'_2)-edge}]
    Suppose, aiming at a contradiction there there is no
    $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
    Notice that there is neither
    a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_2, \nu_2)$-edge (Claim~\ref{claim:no (nu_2, nu_2)-edge})
    nor a $(\nu_2, \nu'_1)$-edge (Claim~\ref{claim:no (nu_2, nu'_1)-edge})
    in $\mathcal{M}$.
    But $|\nu_2| = N_2 > 2N_3 + 2N_4 + 2n + 2k +4$.
    Hence $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no edge below one (nu_2, nu_2)-edge}
    There is
    neither a $(\nu'_1, \nu'_1)$-edge,
    nor a $(\nu'_1, \nu_3)$-edge,
    nor a $(\nu'_1, \sigma')$-edge,
    nor a $(\nu'_1, \nu_4)$-edge
    nor a $(\nu_3, \nu_3)$-edge,
    nor a $(\nu_3, \sigma')$-edge,
    nor a $(\nu_3, \nu_4)$-edge,
    nor a $(\sigma', \sigma')$-edge,
    nor a $(\sigma', \nu_4)$-edge,
    nor a $(\nu_4, \nu_4)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no edge below one (nu_2, nu_2)-edge}]
    Combine Claim~\ref{claim:one (nu_2, nu'_2)-edge} together with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim: all (nu_2, nu'_2)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_2$ $(\nu_2, \nu'_2)$-edge.
    Combing Claim~\ref{claim:no (nu_1, nu_2)-edge} and
    Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    we conclude that there exists a position $a$ in $\nu_2$ that is
    involded in an edge $(a, a')$ in $\mathcal{M}$ that is
    neither a $\nu_1, \nu_2)$-edge,
    nor a $(\nu_2, \nu_2)$-edge.
    Furthermore, according to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:one (nu_4, nu'_4)-edge}
    There is at least $(\nu_4, \nu'_4)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:one (nu_4, nu'_4)-edge}]
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (pi', pi'')-edge}
    There is no $(\pi', \pi'')$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (pi', pi'')-edge}]
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu'_2, pi')-edge}
    There is no $(\nu'_2, \pi')$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu'_2, pi')-edge}]
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu'_3, pi')-edge}]
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu_2, nu'_2)-edge}
    There is no $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_2)-edge}]
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu_3, nu'_3)-edge}
    There is no $(\nu_3, \nu'_3)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_3, nu'_3)-edge}]
    \qed
  \end{proof}
\qed
\end{proof}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{llncsdoc}
\usepackage[english]{babel}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage{shuffle}

@@

  \begin{proof}[of Claim~\ref{claim:one (nu_2, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is no
    $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
    Notice that there is neither
    a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_2, \nu_2)$-edge (Claim~\ref{claim:no (nu_2, nu_2)-edge})
    nor a $(\nu_2, \nu'_1)$-edge (Claim~\ref{claim:no (nu_2, nu'_1)-edge})
    in $\mathcal{M}$.
    But $|\nu_2| = N_2 > 2N_3 + 2N_4 + 2n + 2k +4$.
    Hence $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no edge below one (nu_2, nu'_2)-edge}
    There is
    neither a $(\nu'_1, \nu'_1)$-edge,
    nor a $(\nu'_1, \nu_3)$-edge,
    nor a $(\nu'_1, \sigma')$-edge,
    nor a $(\nu'_1, \nu_4)$-edge
    nor a $(\nu_3, \nu_3)$-edge,
    nor a $(\nu_3, \sigma')$-edge,
    nor a $(\nu_3, \nu_4)$-edge,
    nor a $(\sigma', \sigma')$-edge,
    nor a $(\sigma', \nu_4)$-edge,
    nor a $(\nu_4, \nu_4)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no edge below one (nu_2, nu'_2)-edge}]
    Combine Claim~\ref{claim:one (nu_2, nu'_2)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim: no edge right of nu'_2}
    There is
    neither a $(\nu'_2, \nu'_3)$-edge,
    nor a $(\nu'_2, \pi')$-edge,
    nor a $(\nu'_2, \nu'_4)$-edge,
    nor a $(\nu'_2, \pi'')$-edge
    nor a $(\nu'_2, \sigma'')$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim: no edge right of nu'_2}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ contains an edge $(a, a')$ which is
    either a $(\nu'_2, \nu'_3)$-edge
    or a $(\nu'_2, \pi')$-edge
    or a $(\nu'_2, \nu'_4)$-edge
    or a $(\nu'_2, \pi'')$-edge
    or a $(\nu'_2, \sigma'')$-edge.
    According to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    there exists a $(\nu_2, \nu'_2)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) > \mu(a)$ (since $\nu_2$ is above $\nu'_2$) and
    $\mu(b') < \mu(a')$ (since $\nu'_3$, $\pi'$, $\nu'_4$, $\pi''$ and
    $\sigma''$ are all above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:one (nu_1, nu'_2)-edge}
    There is no $(\nu_1, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:one (nu_1, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is a
    $(\nu_1, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have $b < a$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(b') > \mu(a')$ (since $\nu'_2$ is above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:one (nu'_1, nu'_2)-edge}
    There is no $(\nu'_1, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:one (nu'_1, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is a
    $(\nu'_1, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no edge below one (nu_3, nu'_3)-edge}
    There is
    neither a $(\sigma', \sigma')$-edge,
    nor a $(\sigma', \nu_4)$-edge,
    nor a $(\sigma', \nu'_2)$-edge,
    nor a $(\nu_4, \nu_4)$-edge
    nor a $(\nu_4, \nu'_2)$-edge,
    nor a $(\nu'_2, \nu'_2)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no edge below one (nu_3, nu'_3)-edge}]
    Combine Claim~\ref{claim:one (nu_3, nu'_3)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim: all (nu_2, nu'_2)-edges}]
    According to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    Claim~\ref{}
    all positions in $\nu'_2$ are involved in a $(\nu_2, \nu'_2)$.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (pi', pi)-edge}
    There is no $(\pi', \pi')$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (pi', pi')-edge}]
    Combine Claim~\ref{claim:one (nu_4, nu'_4)-edge} together with the
    fact that $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu'_3, pi')-edge}]
    Suppose aiming at a contradiction that there exists
    a $(\nu'_3, \pi')$-edge $(a, a')$ in $\mathcal{M}$.
    Accordint to Claim~\ref{claim:one (nu_3, nu'_3)-edge},
    there exists a $(\nu_3, \nu'_3)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_3$ is below $\nu'_3$) and
    $\mu(b') > \mu(a')$ (since $\nu'_3$ is above $\pi'$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  Combinf the above claims
\qed
\end{proof}
